\documentclass[12pt, letterpaper, twoside]{article}

\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{color}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{algpseudocode}
\usepackage{enumitem}

\graphicspath{ {./images/} }

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=C,
  aboveskip=2mm,
  belowskip=2mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=2
}

\title{%
Design and Analysis of Algorithms\\
\large 10.3 Social Network Analysis
}
\author{Daniel Shannon}
\date{June 8th, 2022}

\begin{document}
\begin{titlepage}
\maketitle
\end{titlepage}

\section*{10.3.2}
\begin{quote}
  \begin{itemize}
    \item In a real-world social network, how do we find "communities" of people?
    \item E.g., the EECS Department, your soccer team, my extended family
    \item A community is a cluster of nodes: but how do we formalize this?
    \item If you wanted to find these groups, how would you do it?
  \end{itemize}
\end{quote}

As the professor mentioned, my first thoughts drifted towards strongly connected components.
The issue with applying SCCs to this problem is multiple people from one community could
be members of another community. So perhaps we need loosely connected components where 
the cardinality of connections to another community is depended on the number of connections to another loosely connected component.

If the number of connections connecting two loosly connected components is less than both of the 
components, then maybe that would define two communities. There can be overlap between the communities,
but there shouldn't be so much overlap that they are one component.

\section*{10.3.6}
\begin{quote}
  Suppose you are given an adjacency matrix.
  How would you calculate the number of common neighbors that two nodes have?
\end{quote}

I would count the values between the $i_{nodeA}$ and $i_{nodeB}$ row and the $j_{nodeA}$ and $j_{nodeB}$ column. Any values in the column and row should be common neighbors?

\end{document}
