\documentclass[12pt, letterpaper, twoside]{article}

\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{color}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{algpseudocode}
\usepackage{enumitem}

\graphicspath{ {./images/} }

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=C,
  aboveskip=2mm,
  belowskip=2mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=2
}

\title{%
Design and Analysis of Algorithms\\
\large 9.3 Dealing with hard problems
}
\author{Daniel Shannon}
\date{May 25th, 2022}

\begin{document}
\begin{titlepage}
\maketitle
\end{titlepage}

\section*{9.3.2}
\begin{itemize}
    \item Brute force solution: Try every possivle solution and find the best.
    \item How long does this take for the following? Assume problem size is N.
    \begin{itemize}
        \item Minimum Spanning Tree
        $E^N$
        \item Traveling salesman
        $N!$
        \item SAT
        $2^N$
    \end{itemize}
\end{itemize}

\section*{9.3.4}
\begin{itemize}
    \item A Hamiltonian cycle is a cycle that visits every vertex exactly once.
    \item Brute force: n! possible cycles.
    \item Design a more efficient backtracking algorithm.
\end{itemize}

Similar to backtracking for SAT, we can start searching at a node and mark each neighboring node
as explored or not. If the explored node connects with another explored node, we stop searching.
I think maybe the tallest branch with a height of V or V-1 of the resulting tree would a the Hamiltonian cycle.

\section*{9.3.6}
\begin{itemize}
    \item You have an N x N chessboard.
    \item You want to place N queens on the chessboard so that no two queens are in the same row or column.
    \item Brute force: $N^{2N}$
    \item Design a more efficient backtracking algorithm.
\end{itemize}

We could start at a vertex $v$ and begin a search. 
Any vertex that is directly in line or diagonal to the current vertex can be a termination
point on the tree. Now how to do this optimally...? Maybe include back, cross, and forward edges.


\section*{9.3.8}
\begin{itemize}
    \item You are given a weighted graph.
    \item Find a least-cost cycle that visits every node exactly once.
    \item In the naïve brute-force algorithm, how many possible cycles are there?
    \item Design a branch-and-bound solution to the traveling salesman problem.
\end{itemize}

This is similar to the hamiltonian cycle problem, but with each node bound by a budget.
Starting at $v_i$, we can explore each of the paths and determine the next node $v_{i+1}$
and determine which will use the least of the available budget. So at each step we are 
looking for the smallest budget to be removed and we can remove branches of the search tree.


\end{document}
