\documentclass[12pt, letterpaper, twoside]{article}

\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{color}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{algpseudocode}
\usepackage{enumitem}

\graphicspath{ {./images/} }

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=C,
  aboveskip=2mm,
  belowskip=2mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=2
}

\title{%
Design and Analysis of Algorithms\\
\large 8.4 NP-Completeness
}
\author{Daniel Shannon}
\date{May 26th, 2022}

\begin{document}
\begin{titlepage}
\maketitle
\end{titlepage}

\section*{8.3.2}
\begin{quote}
\begin{itemize}
    \item MaxClique: A clique in a graph is a set of nodes $S$ such that every node in $S$ is connected to every other node in $S$.
    \item Given a graph, what is the largest clique that it contains?
    \item Show that MaxClique is NP-hard by reducing 3SAT to MaxClique.
    \item 3SAT$\rightarrow{MC}$
\end{itemize}

\end{quote}

1. 3SAT is NP-Complete
2. 3SAT reduces to MaxClique in a similar way to 2SAT reduces to 3SAT.

$(x\lor{y}\lor{y}\lor{z}\lor{...})\land{(x\lor{y}\lor{y}\lor{z}\lor{...})}\land{(x\lor{y}\lor{y}\lor{z}\lor{...})}$

I'm really blanking on this. What I think we would do is break out
3SAT into groups of $\lor$ statements $(x\lor{y}\lor{y}\lor{z}\lor{A})(x\lor{y}\lor{y}\lor{z}\lor{A})\lor{(x\lor{y}\lor{y})}\lor{({z}\lor{A})}$


Is this conversion polynomial time? Yes
Is getting the solution back polynomial? Yes
If there is a solution to SAT3 is there a solution to MC?
Vica versa?
\end{document}
